\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-08-07 manuscript/main.tex
modified:   manuscript/Platform-Mediated Consolidation and Offline Store Expansion.pdf 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results. To address this, a ``Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities. In this study, we apply a Donut Hole robustness check to an RDD with a cutoff of 410 meters. Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect. The distances considered for exclusion are 5, 7.5, 10, 12.5, 15, 17.5, 20 meters, and they are correspondingly dropping 7.85\%, 11.73\%, 15.59\%, 19.48\%, 23.66\%, 27.88\% and 31.71\% of our effective estimation data, respectively. Appendix Table \ref{tab:rd_robust_results} indicate that up to the exclusion of 20\% of the estimated data, the treatment effect estimates remain consistent and robust, thereby demonstrating the robustness of the estimated treatment effects to the exclusion of data points near the cutoff. Moreover, we find that adding control variables may help us to better estimate the treatment effect and make our model more robust.

>>>>

One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results. To address this, a falsification testing based on ``Donut Hole'' specifications can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities. 
In this study, we conduct a robustness check using the Donut Hole method on a RDD with a cutoff at 410 meters. Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect. The distances considered for exclusion are 5, 7.5, 10, 12.5, 15, 17.5, 20 meters, and they are correspondingly dropping 7.85\%, 11.73\%, 15.59\%, 19.48\%, 23.66\%, 27.88\% and 31.71\% of our effective estimation data, respectively. Appendix Table \ref{tab:rd_robust_results} indicate that up to the exclusion of 20\% of the estimated data, the treatment effect estimates remain consistent and robust, thereby demonstrating the robustness of the estimated treatment effects to the exclusion of data points near the cutoff. Moreover, we find that adding control variables may help us to better estimate the treatment effect and make our model more robust.
